---
title: "Alcohol vs Seat choice"
author: "Mairani"
date: "summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
#Introduction 

 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
you choose to sit in??

The data came from UCDavis.

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

#Methods
In the data set davidsdata Seat is a categorical variable and alcohol is numerical.

We try to predict alcohol based on seats so we use the helper file numerical~cat.rmd.

# results

## descriptive results

### graphical summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
This boxplot shows that alcohol is most increased when a seat is at the back.

### numerical summary
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The table shows that the back seats have the highest alcohol because its average is the highest and it has the highest maximum as well.

### Inferential results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p-value is 0.00116, less than 0.05 so we reject the null hypothesis.
In other words, there is a difference in alcohol consumption based on seats.

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```
## Conclusions


