---
title: "Alcohol vs Seat choice"
author: "Mairani"
date: "summer 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
#Introduction 

 Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
you choose to sit in??

The data came from UCDavis.

$H_0$: There is no difference between the average number of drinks imbibed between people conditioned on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

#Methods
In the data set davidsdata Seat is a categorical variable and alcohol is numerical.

We try to predict alcohol based on seats so we use the helper file numerical~cat.rmd.

# results

## descriptive results

### graphical summary

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```

This boxplot shows that alcohol is most increased when a seat is at the back.  

### numerical summary
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The table shows that the back seats have the highest alcohol because its average is the highest and it has the highest maximum as well.   

### Inferential results

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The p-value is 0.00116, less than 0.05 so we reject the null hypothesis.
In other words, there is a difference in alcohol consumption based on seats.   

## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```

The Tukey test shows that the chance of alcohol consumption decreases as it approaches the front seat.   

## Conclusions

The inferential graph shows that the p-value is 0.00116, less than 0.05. This means that the null hypothesis is rejected as the value is too small and doesn't prove that there is no difference between the average number of drinks imbibed between people conditioned on the row they sit in. The tukey test and the numerical summary also prove that average number drinks is different between at least two rows.

 To conclude, the inferential analysis conducted having a p-value of 0.00116 ( less than the significance level of 0.05), tells us we reject the null hypothesis.
